---
title: "Lab 11 - Smoking during pregnancy"
author: "Colin Li"
date: "4/4/2023"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(infer)
library(openintro)
library(Hmisc)
library(psych)
library(plyr)
library(boot)
data(ncbirths)


```

### Exercise 1

```{r}

multi.hist(ncbirths[,sapply(ncbirths, is.numeric)])


```
cases are births recorded in NC, there are 1000 cases


### Exercise 2

```{r}

ncbirths_white <- ncbirths %>% 
  filter(whitemom == "white")

mean(ncbirths_white$weight)

```
### Exercise 3

```{r}

# save resulting bootstrap distribution
boot_df <- ncbirths_white %>%
  # specify the variable of interest
  specify(response = weight) %>% 
  # generate 15000 bootstrap samples
  generate(reps = 35000, type = "bootstrap") %>% 
  # calculate the mean of each bootstrap sample
  calculate(stat = "mean")

boot_df

mean(boot_df$stat)

ggplot(data = boot_df, mapping = aes(x = stat)) +
  geom_histogram(bins = 30, color = "#000000", fill = "#0099F8") + theme_classic() + labs(title = "A Bootstrap Distribution of Sample Means", subtitle = "Replicates = 35000")


boot_n <- boot_df %>%
  mutate(null = stat
         + 0.179406)

mean(boot_n$null)

```

### Exercise 4

```{r}


ggplot(data = boot_n, mapping = aes(x = null)) +
  geom_histogram(bins = 30,  color = "#000000", fill = "#0099F8") + theme_classic() + labs(title = "A Null Distribution of Sample Means") 

t.test(boot_n$stat, boot_n$null)


```

There is a significant difference in baby weights between 1995 and after. 

### Exercise 5

```{r}

ncbirths_clean <- ncbirths %>%
  filter(habit != "" & weight != "")


```

### Exercise 6

```{r}

ggplot(data = ncbirths_clean, aes(x= habit, y= weight)) + geom_boxplot(fill = "#0099F8") + theme_classic()

```


### Exercise 7

```{r}

ncbirths_clean %>%
  group_by(habit) %>%
  summarise(mean_weight = mean(weight))

```

### Exercise 8

H0: nonsmokers and smokers' babies have the same weight on average ( μ 1 = μ 2 ), HA: nonsmokers and smokers' babies do not have the same weight on average ( μ 1 ≠ μ 2 )


### Exercise 9

```{r}

t.test(ncbirths_clean$weight ~ ncbirths_clean$habit)

```
p = .019, so there is a significant difference in baby weights between smokers and nonsmokers. Looking at the means, nonsmokers' babies weigh more than smokers'. 

### Exercise 10

95 percent confidence interval:
 0.05151165 0.57957328
 
### Exercise 11

```{r}

ggplot(data = ncbirths, aes(x =mature, y =mage)) + geom_count(color = "#0099F8", alpha = 0.3) + theme_classic()

ggplot(data = ncbirths, aes(x =lowbirthweight, y =weight)) + geom_count(color = "#0099F8", alpha = 0.1) + theme_classic()

```
My method is to plot the data then view the file. It looks like the mom's age at 35 is the cutoff, below 35 are considered younger moms, 35 and above are considered mature moms. 
For low weight, it looks like 5.5 is the cut off, 5.5 and below are considered low weight, above 5.5 are considered not low weight. 

### Exercise 12

```{r}

#H0: the proportion of low birth weight babies for younger mothers is the same as for mature mothers. HA: the proportion of low birth weight babies is higher for mature mothers than for younger mothers.

ncbirths %>%
  filter(mature == "younger mom") %>%
  group_by( lowbirthweight ) %>%
  dplyr::summarise(percent = 100 * n() / nrow(ncbirths))

  
ncbirths %>%
  filter(mature == "mature mom") %>%
  group_by( lowbirthweight ) %>%
  dplyr::summarise( percent = 100 * n() / nrow( ncbirths ) )


```

I feel like my code for the last assignment is not really correct :( but I did it to my best ability